An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-08-05 CMPSpaper_writing/CMPSpaper_writing.Rmd
added pipeline code for hamby44

dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
  geom_tile() + 
  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
  ylab("Bullet2 Lands") + 
  geom_text(aes(label=cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

>>>>

dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
  geom_tile() + 
  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
  ylab("Bullet2 Lands") + 
  geom_text(aes(label=cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
# dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score/cmps_nseg)) +
#   geom_tile() +
#   geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) +
#   scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6/25) +
#   scale_colour_manual("Source", values="darkorange") +
#   facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") +
#   ylab("Bullet2 Lands") +
#   geom_text(aes(label=round(cmps_score/cmps_nseg, digits = 2))) +
#   theme_bw() +
#   theme(aspect.ratio = 1)
```
